---
title: "Large Scale Code Embedding with Applications to Feature Selection and Knowledge Discovery in Electronic Health Records"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The increasing availability of Electronic Health Record (EHR) systems has created enormous potential for translational research. While the huge amount of information in EHR can be used in clinical informatics tasks, data mining for EHR data with complex structure is challenging. Traditional data mining approaches require domain knowledge to select relevant codes, which hampers the efficiency for translational research. In this project, we aim to using large scale code embeddings to facilitate effective feature selection and knowledge discovery with EHR data.

## Installation

Install development version from GitHub.

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("celehs/embedFS")
```

Load the package into R.

```{r}
library(embedFS)
```

```{r}
data <- readRDS(url("https://github.com/celehs/embedFS/raw/master/embed/embed.rds", "rb"))
str(data)
```

